19Q2

### 2020-01-10 19Q2.Rmd
update manuscript figures with restricted heatmaps, add prelim KS test res to Rmd

ccle_signif_dgl %>% count(InG2P)
filter(ccle_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
ctrp_signif_dgl %>% count(InG2P)
filter(ctrp_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
gdsc_signif_dgl %>% count(InG2P)
filter(gdsc_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
```

@@

gdsc_signif_prot_lin <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)

# ccle_signif_prot_lin %>% count(InG2P)
# filter(ccle_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
# ctrp_signif_prot_lin %>% count(InG2P)
# filter(ctrp_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
# gdsc_signif_prot_lin %>% count(InG2P)
# filter(gdsc_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
```

@@

## Data summaries

@@

```{r fig.height=10, fig.width=10}
slices <- ccle_disease_n$n
lbls <- paste0(ccle_disease_n$disease_g2p, " (", round(ccle_disease_n$percent, digits = 2), "%)")
pie(slices,labels = lbls, col = ccle_disease_n$color, radius = 0.5)
```

@@

```{r supp_stats, eval=FALSE}
maf_g2p_summ_gene <- maf_g2p %>% group_by(Gene) %>% count(Mutation) %>% filter (Mutation == 1) %>% merge(unique(select(maf_g2p, DepMap_ID, Gene)) %>% count(Gene), by = "Gene", suffixes = c("_mut", "_cell_lines"), all = TRUE)
maf_g2p_summ_gene$PercCellLinesMutated <- maf_g2p_summ_gene$n_mut/maf_g2p_summ_gene$n_cell_lines * 100

maf_g2p_summ <- maf_g2p %>% group_by(disease) %>% count(Mutation) %>% filter (Mutation == 1) %>% merge(unique(select(maf_g2p, DepMap_ID, disease)) %>% count(disease), by = "disease", suffixes = c("_mut", "_cell_lines"), all = TRUE)
maf_g2p_summ$MutPerCCL <- maf_g2p_summ$n_mut/maf_g2p_summ$n_cell_lines

sum(maf_g2p_summ$n_cell_lines)
777/1588
sum(maf_g2p_summ$n_mut[!is.na(maf_g2p_summ$n_mut)])
2067/3151
```

@@

```{r}
ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")

@@

```{r}
ccle_mut_lin <- filter(ccle_signif_dgl, InG2P == "Yes")
ctrp_mut_lin <- filter(ctrp_signif_dgl, InG2P == "Yes")
gdsc_mut_lin <- filter(gdsc_signif_dgl, InG2P == "Yes")

>>>>

# ccle_signif_dgl %>% count(InG2P)
# filter(ccle_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
# ctrp_signif_dgl %>% count(InG2P)
# filter(ctrp_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
# gdsc_signif_dgl %>% count(InG2P)
# filter(gdsc_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
# library(spatstat)
```

@@

gdsc_signif_prot_lin <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)
```

@@

## KS tests

**1/10/20: Restrict datasets to heatmap drug-genes and run KS tests.**
```{r}
ks.test(filter(ccle_signif_g2p_dg, InG2P == "Yes")$p, filter(ccle_signif_g2p_dg, InG2P == "No")$p)
ks.test(filter(ctrp_signif_g2p_dg, InG2P == "Yes")$p, filter(ctrp_signif_g2p_dg, InG2P == "No")$p)
ks.test(filter(gdsc_signif_g2p_dg, InG2P == "Yes")$p, filter(gdsc_signif_g2p_dg, InG2P == "No")$p)

ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)
ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)
ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)

ks.test(filter(ccle_signif_prot, InG2P == "Yes")$p, filter(ccle_signif_prot, InG2P == "No")$p)
ks.test(filter(ctrp_signif_prot, InG2P == "Yes")$p, filter(ctrp_signif_prot, InG2P == "No")$p)
ks.test(filter(gdsc_signif_prot, InG2P == "Yes")$p, filter(gdsc_signif_prot, InG2P == "No")$p)

ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)
ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)
ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)

ks.test(filter(cn_cor, Dataset == "CCLE" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "CCLE" & InG2P == "No")$CN_p)
ks.test(filter(cn_cor, Dataset == "CTRP" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "CTRP" & InG2P == "No")$CN_p)
ks.test(filter(cn_cor, Dataset == "GDSC" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "GDSC" & InG2P == "No")$CN_p)

ks.test(filter(ge_cor, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "CCLE" & InG2P == "No")$GE_p)
ks.test(filter(ge_cor, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "CTRP" & InG2P == "No")$GE_p)
ks.test(filter(ge_cor, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "GDSC" & InG2P == "No")$GE_p)

ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)
ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)
ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)

ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)
ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)
ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)
```

## Data summaries/Supp

@@

```{r fig.height=3, fig.width=3}
slices <- ccle_disease_n$n
lbls <- paste0(ccle_disease_n$disease_g2p, " (", round(ccle_disease_n$percent, digits = 2), "%)")
pie(slices,labels = lbls, col = ccle_disease_n$color, radius = 0.5)
```

@@

Of the top 10 most cited genes in G2P (Figure 1), 50% were also found in the top 10 most frequently mutated across all 1588 tested cell lines
```{r supp_stats, eval=FALSE}
ccls <- union(union(unique(ccle$DepMap_ID), unique(ctrp$DepMap_ID)), unique(gdsc$DepMap_ID))

maf_g2p_summ_gene <- filter(maf_df, DepMap_ID %in% ccls & Gene %in% unique(g2p_mut$Gene)) %>% group_by(Gene) %>% count(Mutation) %>% filter (Mutation == 1) %>% mutate(percent = n / length(ccls) * 100)
g2p_summ_gene <- g2p_mut %>% count(Gene) %>% mutate(percent = n / nrow(g2p_mut) * 100)

maf_g2p_summ_lin <- merge(filter(maf_df, DepMap_ID %in% ccls & Gene %in% unique(g2p_mut$Gene)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% group_by(disease) %>% count(Mutation) %>% filter (Mutation == 1)
maf_g2p_summ_lin$percent <- with(maf_g2p_summ_lin, n / sum(n) * 100)

g2p_summ_lin <- g2p %>% count(disease) %>% mutate(percent = n / nrow(g2p) * 100)

ccl_summ_lin <- filter(ccl_meta, DepMap_ID %in% ccls) %>% count(disease)
ccl_summ_lin$percent <- with(ccl_summ_lin, n / sum(n) * 100)
```

@@

```{r, eval=FALSE}
ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")

@@

```{r, eval=FALSE}
ccle_mut_lin <- filter(ccle_signif_dgl, InG2P == "Yes")
ctrp_mut_lin <- filter(ctrp_signif_dgl, InG2P == "Yes")
gdsc_mut_lin <- filter(gdsc_signif_dgl, InG2P == "Yes")
